---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# blblm

<!-- badges: start -->
<!-- badges: end -->

The goal of blblm is to implement the linear regression with little bag of bootstraps by using blblm(formula,data,parallel,m,B)

## Installation

You can install the released version of blblm from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("blblm")
```

And the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("XiaoqiNa/blblm")
```

## Examples

This is a basic example which shows you how to solve a common problem via `blblm`:

Fiting a linear regression model in the bag of little bootstraps via `blblm`:

```{r}
library(blblm)
fit <- blblm(formula=Sepal.Length~Petal.Length+Petal.Width,data=iris,m=10,B=100,parallel=TRUE)
```

Computting the coefficient of the blblm via `coef.blblm`:
```{r}
coef.blblm(fit)
```

Getting the confidence interval at the level alpha=0.05 of blblm via `confint.blblm`:
```{r}
confint.blblm(fit,parm = NULL, level = 0.95)
```

Computing the predict model for the blblm via `predict.blblm`:
```{r}
predict.blblm(fit,data.frame(Petal.Length=c(3.0,5.0),Petal.Width=c(0.1,1.1)),confidence=TRUE,level=0.95)
```
